---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  echo = FALSE
)

embed_png <- function(image_title, width = "100%") {
  knitr::asis_output(
    glue::glue("<div style=\"text-align: center; padding: 2rem 0;\">",
                 "<img src=\"man/figures/{image_title}\" width={width} />",
               "</div>")
  )
}
```


# Adjustr v0.5.0.0

<!-- badges: start -->
<!-- badges: end -->

The goal of Adjustr is to easily fit a given random variable in order to find it's distribution.

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("moutikabdessabour/adjustr")
```

# Using it

The package is made up of two main functions.

## getfitdistr

To fit continuous random variables
```{r, eval=F}
getfitdistr(x, 
            short=TRUE, 
            showplots=TRUE,
            plots.as.vars=FALSE, 
            xlab="Claim amounts",
            color=c(gamma = "steelblue", lognormal="firebrick",exponential= "green"))
```

The available arguments are: 

| Argument | Description |
| -------- | ----------- |
|`short` | when used the function will return only the best fitted distribution if it exists |
|`x`     | The vector that contains the values of the continuous random variable |
|`showplots` | Whether To show the plots or not |
|`plots.as.vars`     | Whether you want to add the plots to the result |
|`xlab`    | what do you want to name the X axis? |
|`color`  |The color you want to use in the plots |

This code is all that's needed to fit your random variable, the returned value is a list. let `distribution` be the name of a distribution we have:

|  File    |  Description |
| ----     | ----         |
|`dirtibutions`    | The distribution that the code looped through. |
|`acceptedDistr` | A `data.frame` that contains the distributions that verify the null hypothesis order from the lowest **AIC** to the biggest. |
| `distribution` | A list containing the `$estimate` for said distribution, the `$p.value` for the Kolmogorov-Smirnov test, `$accepthyp` when the Null Hypothesis is accepted or not and `$aic` containing the *Akaike information criterion* for this distribution. |
|`bestdistr`| the best fitted distribution|

## getgoodfit

To fit discrete random variables:
```{r, eval=F}
getgoodfit(x, showplots=F, short=TRUE, plots.as.vars=F, xlab="Number of claims")
```

The available arguments are: 

| Argument | Description |
| -------- | ----------- |
|`short` | when used the function will return only the best fitted distribution if it exists |
|`x`     | The vector that contains the values of the discrete random variable |
|`showplots` | Whether To show the plots or not |
|`plots.as.vars`     | Whether you want to add the plots to the result |
|`xlab`    | what do you want to name the X axis? |

This code is all that's needed to fit your random variable, the returned value is a list. let `distribution` be the name of a distribution we have:

|  File    |  Description |
| ----     | ----         |
|`dirtibutions`    | The distribution that the code looped through. |
|`acceptedDistr` | A `data.frame` that contains the distributions that verify the null hypothesis order from the lowest **Chi-squared** to the biggest. |
|`distribution` | A list containing the `$estimate` for said distribution, the `$observed` and `$fitted` values, the `$count` and the `$prob`, the `$p.value`, `$Xsquared` and the `$df` degrees of freedom for the Chi-squared test, `$accepthyp` when the Null Hypothesis is accepted or not. |
|`bestdistr`| the best fitted distribution|

# Questions?

Confused by anything (there's a lot to be confused by)? [Open an issue on github](https://github.com/moutikabdessabour/adjustr/issues/new) and let me know.
